Motivating Exploration in Reinforcement Learning

### 2020-04-16 paper/main.tex
fixed e

And yet, even with the massive computational resources available today, the most impressive artificial learning agents struggle tremendously in balancing explicit exploration of the environment and stable convergence towards a useful, learned policy. Without adequate exploration and randomness, the agent can easily become stuck and converge towards a flawed policy early on in learning; the agent's policy reflects high certainty on its understanding of the environment when, in reality, it has yet to explore the majority of the state space. On the other hand, Excessive exploration can lead to unstable rewards and updates throughout learning which are detrimental to learning a useful policy. To make matters worse, there is a huge breadth of algorithms and hand-crafted techniques used in reinforcement learning, many of them requiring method or task specific hyperparameter tuning. This in turn leads to very specialized formulations across the field for encouraging exploration.

>>>>

And yet, even with the massive computational resources available today, the most impressive artificial learning agents struggle tremendously in balancing explicit exploration of the environment and stable convergence towards a useful, learned policy. Without adequate exploration and randomness, the agent can easily become stuck and converge towards a flawed policy early on in learning; the agent's policy reflects high certainty on its understanding of the environment when, in reality, it has yet to explore the majority of the state space. On the other hand, excessive exploration can lead to unstable rewards and updates throughout learning which are detrimental to learning a useful policy. To make matters worse, there is a huge breadth of algorithms and hand-crafted techniques used in reinforcement learning, many of them requiring method or task specific hyperparameter tuning. This in turn leads to very specialized formulations across the field for encouraging exploration.
